---
title: "Statistical Inference Project Part 1 - Saran Shanmugam"
output: pdf_document
---
#Overview
This Coursera-Statistical Inference(Data Science Specialization) project illustrates 
1. A Simulation exercise.
2. Basic Inferential Data Analysis.

#Synopsis
The exponential distribution in R here is demonstrated using rexp() function with exponentials of 40 and lambda of 0.2 for a 1000 observations.

#Results

##Simulations
Lets generate 1000 simulated averages for 40 exponentials and lambda of 0.2 using rexp()

```{r}
library(ggplot2)
library(knitr)
numsim <- 1000
lambda <- 0.2
sample <- 40
set.seed(123)
mns=NULL
for(i in 1:1000) mns=c(mns,mean(rexp(sample,lambda)))
par(mar=rep(2,4))
hist(mns,main="Distribution of averages of samples")
```

##1. Sample Mean versus Theoretical Mean
The next step is comparing the theortical and sample mean
```{r}
actual_mean <- round(mean(mns),3)
theory_mean <- 1/lambda
print(paste("Sample Mean=",actual_mean))
print(paste("Theoretical Mean=",theory_mean))
```

Looking at both the means,they are approximately the same. 

 
##2. Sample Variance versus Theoretical Variance
The next step is comparing the theortical and sample variance
```{r}
actual_var <- round(var(mns),3)
theory_var <- (1/lambda)^2/sample
print(paste("Sample Variance=",actual_var))
print(paste("Theoretical Variance=",theory_var))
```

From above, it can be infered that the Sample and Theoretical variances are almost the same. 

##3. Demonstration that the distribution is approximately normal

The last step is demonstrating that the distribution is approximately normal 

```{r}
mns_df <- data.frame(mns)
gg <- ggplot(mns_df,aes(x=mns))
gg <- gg + geom_bar(aes(y=..density..),colour="black",fill="green",binwidth=.2)
gg <- gg + geom_density(colour="blue",size=2)
gg
```

The above plot depicts a distribution of approximately normal 